The \textit{Kepler} Smear Campaign

### 2019-03-15 paper/ms.tex
final?

To facilitate open science, we have made the products of this research available online. All code used to produce smear light curves is available under a GPL~v3 license at \url{github.com/benjaminpope/keplersmear}. All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main-sequence stars as discussed in Sections~\ref{mainseq} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product. TRES spectra will be made available from the ExoFOP-TESS website, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.

All smear light curves in this paper, as well as the \LaTeX{} source code used to produce this document, can be found
at \url{github.com/benjaminpope/smearcampaign}.

@@

The \kepler Smear Campaign establishes a legacy sample of~102 very bright stars, with \kepler light curves that in almost all cases reveal astrophysically interesting variability. The virtue of these bright stars is that they can be studied with interferometry, and more easily with spectroscopy than fainter targets, permitting especially detailed characterization. These stars will also be bright enough to be re-observed with high precision by the Transiting Exoplanet Survey Satellite \citep[][TESS;]{tess}. We have obtained detailed abundances of a subset of the red giants in this sample, with a view to confirming their membership of the Galactic thick and thin disk populations. A compelling next step is to use interferometric diameter measurements and to further constrain the red giant parameters, and compare these to the constraints from \gaia. Any tension between these measurements will help test and refine the asteroseismic scaling relations, and better models will propagate through to smaller systematic uncertainties in large samples of stars too faint for interferometry. Further improvements will be revealed by the detailed modelling of individual oscillation frequencies in these giants to infer interior structure such as convective overshoot. For the lower-frequency M~giants classed as LPVs in this paper, extending the systematics correction and quarter-stitching algorithms to more robustly correct their light curves without removing real signal will allow similar asteroseismic analysis, for a sample of stars that are much less well understood than their higher-frequency counterparts.

>>>>

To facilitate open science, we have made the products of this research available online. All code used to produce smear light curves is available under a GPL~v3 license at \href{https://github.com/benjaminpope/keplersmear}{\nolinkurl{github.com/benjaminpope/keplersmear}}. All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main-sequence stars as discussed in Sections~\ref{mainseq} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product. TRES spectra will be made available from the ExoFOP-TESS website, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.

All smear light curves in this paper, as well as the \LaTeX{} source code used to produce this document, can be found
at \href{https://github.com/benjaminpope/smearcampaign}{\nolinkurl{github.com/benjaminpope/smearcampaign}}.

@@

The \kepler Smear Campaign establishes a legacy sample of~102 very bright stars, with \kepler light curves that in almost all cases reveal astrophysically interesting variability. The virtue of these bright stars is that they can be studied with interferometry, and more easily with spectroscopy than fainter targets, permitting especially detailed characterization. These stars will also be bright enough to be re-observed with high precision by the Transiting Exoplanet Survey Satellite \citep[TESS;][]{tess}. We have obtained detailed abundances of a subset of the red giants in this sample, with a view to confirming their membership of the Galactic thick and thin disk populations. A compelling next step is to use interferometric diameter measurements and to further constrain the red giant parameters, and compare these to the constraints from \gaia. Any tension between these measurements will help test and refine the asteroseismic scaling relations, and better models will propagate through to smaller systematic uncertainties in large samples of stars too faint for interferometry. Further improvements will be revealed by the detailed modelling of individual oscillation frequencies in these giants to infer interior structure such as convective overshoot. For the lower-frequency M~giants classed as LPVs in this paper, extending the systematics correction and quarter-stitching algorithms to more robustly correct their light curves without removing real signal will allow similar asteroseismic analysis, for a sample of stars that are much less well understood than their higher-frequency counterparts.
